% ============================================================
%  Yuan Shan — Curriculum Vitae (full, multi-page)
%  Compile with: tectonic cv.tex
% ============================================================
\documentclass[11pt,letterpaper]{article}

\usepackage[margin=0.85in,top=0.8in,bottom=0.8in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{lastpage}

\renewcommand{\familydefault}{\sfdefault}

% ---------- palette ----------
\definecolor{accent}{HTML}{8A3324}
\definecolor{ink}{HTML}{1C1C21}
\definecolor{muted}{HTML}{555560}
\definecolor{soft}{HTML}{8A8A95}

\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent, pdftitle={Yuan Shan -- CV}, pdfauthor={Yuan Shan}}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ---------- page numbers (footer) ----------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\small\color{soft} Yuan Shan \;\textbar\; CV \;\textbar\; Page \thepage\ of \pageref{LastPage}}

% ---------- section style ----------
\titleformat{\section}
  {\large\bfseries\color{accent}}
  {}{0pt}{}
  [\vspace{-6pt}{\color{accent}\rule{\textwidth}{0.7pt}}]
\titlespacing*{\section}{0pt}{18pt}{8pt}

\titleformat{\subsection}
  {\normalsize\bfseries\color{ink}}
  {}{0pt}{}
\titlespacing*{\subsection}{0pt}{8pt}{2pt}

% ---------- list defaults ----------
\setlist[itemize]{
  leftmargin=1.2em,
  topsep=2pt,
  parsep=0pt,
  itemsep=2pt,
  label=\textcolor{accent}{\textbullet}
}

% ---------- entry helper ----------
\newcommand{\entry}[4]{%
  \noindent\textbf{\color{ink}#1}\hfill{\color{soft}\small #3}\\[1pt]%
  \textit{\color{muted}#2}\hfill\textit{\color{soft}\small #4}%
  \vspace{2pt}%
}

\begin{document}

% ============== HEADER ==============
\begin{center}
  {\fontsize{30}{34}\selectfont\bfseries\color{ink} Yuan Shan}\\[6pt]
  {\small\color{muted} Master of Statistical Science Student\, $\cdot$\, Duke University}\\[8pt]
  {\small\color{muted}
    \href{mailto:ys328@duke.edu}{ys328@duke.edu}
    \;\textbar\; (919) 697-2488 (US) / +86 159-1080-1104 (CN) \;\textbar\;
    \href{https://github.com/cedricshan}{github.com/cedricshan}
  }\\[2pt]
  {\small\color{muted}
    \href{https://www.linkedin.com/in/yuanshan20011218/}{linkedin.com/in/yuanshan20011218}
    \;\textbar\;
    \href{https://cedricshan.github.io}{cedricshan.github.io}
  }
\end{center}

% ============== EDUCATION ==============
\section{EDUCATION}

\entry{Duke University}{M.S.\ in Statistical Science}{Aug 2024 -- May 2026}{Durham, NC, USA}
\\[3pt]
\entry{Duke University}{B.S.\ in Interdisciplinary Studies --- Data Science}{Jul 2020 -- Aug 2024}{Durham, NC, USA}
\\[3pt]
\entry{Duke Kunshan University}{B.S.\ in Data Science}{Jul 2020 -- Aug 2024}{Kunshan, China}

% ============== RESEARCH INTERESTS ==============
\section{RESEARCH INTERESTS}
\noindent\color{muted}
Large language models, reinforcement learning (RLHF, GRPO), self-evolving language model agents, statistical modeling, causal machine learning, design of experiments.

% ============== PUBLICATIONS ==============
\section{PUBLICATIONS}

\noindent
Z.~Ma$^{*}$, \textbf{\color{ink}Yuan Shan}$^{*}$, J.~Zhao, N.~Xu, L.~Wang.
\textit{``MEOW: End-to-End Outline Writing for Automatic Academic Survey.''}
\textbf{IEEE International Conference on Acoustics, Speech, and Signal Processing (ICASSP), 2026.}
\;\href{https://ieeexplore.ieee.org/document/11462654}{[IEEE Xplore]}\;
\href{https://arxiv.org/abs/2509.19370}{[arXiv]}\;
\href{https://github.com/cedricshan/Survey-Outline-Evaluation-Benckmark}{[Code \& Benchmark]}
\hfill {\small\color{soft}\textit{$^{*}$ Equal contribution.}}

\vspace{4pt}
{\small\color{muted}
Reformulates survey outline writing as an end-to-end task that maps paper metadata to a hierarchical outline. Curates a high-quality dataset distilled from 2.82M arXiv, 252k bioRxiv, and 72k medRxiv records, with Chain-of-Thought reasoning chains generated via DeepSeek-R1. Trains an 8B reasoning model (Qwen3-8B) in two stages: SFT cold-start followed by GRPO with a Tree-Edit-Distance structural reward and a format-compliance reward. Establishes an LLM-as-a-Judge benchmark covering five criteria (Structure Locate / Detail, Content Exclusion / Depth, Pragmatics Concise) plus a structural-distance metric. \textbf{Meow-8B-SFT-GRPO} surpasses SurveyX (35.62 vs.\ 29.60 LLM-Judge total) and outperforms GPT-5 Nano, DeepSeek-R1, and Gemini 2.5 Flash-Lite on the SurveyX test set.}

% ============== WORKING PAPERS ==============
\section{WORKING PAPERS}

\noindent
\textbf{\color{ink}Self-Evolving LLM Agent.} \textit{In preparation.}\\[2pt]
{\small\color{muted}\itshape Research project on reinforcement-learning-driven self-evolution for large language model agents.}

% ============== EXPERIENCE ==============
\section{INDUSTRY \& RESEARCH EXPERIENCE}

\entry{Wenge Tech \,\textemdash\, LLM Algorithm Engineer Intern}{Beijing, China}{May 2025 -- Oct 2025}{}\\[1pt]
{\small\color{accent}\itshape Work accepted at IEEE ICASSP 2026 (co-first author)}
\begin{itemize}
  \item Co-designed and built \textbf{MEOW}, the first metadata-driven, end-to-end LLM framework that maps paper metadata to hierarchical academic survey outlines in a single inference step, replacing prior multi-agent template workflows that produce shallow, rigid outlines.
  \item Built the data pipeline that curated and filtered \textbf{2.82M arXiv}, \textbf{252k bioRxiv}, and \textbf{72k medRxiv} records into a high-quality survey dataset; enriched references via vector retrieval (\texttt{all-MiniLM-L6-v2}) and distilled Chain-of-Thought reasoning chains using \textbf{DeepSeek-R1} to bridge metadata input and outline output.
  \item Trained \textbf{Qwen3-8B} in two stages: SFT cold-start on the CoT-annotated corpus, followed by Group Relative Policy Optimization (\textbf{GRPO}) with a Tree-Edit-Distance \textit{structural similarity reward} and a binary \textit{format-compliance reward}, weighted by $\lambda$.
  \item Established an LLM-as-a-Judge evaluation framework covering five criteria (Structure Locate / Detail, Content Exclusion / Depth, Pragmatics Concise) plus a structural-distance metric; released the benchmark, training corpus, and evaluation scripts publicly on Hugging Face and GitHub.
  \item Used \textbf{vLLM} to accelerate both inference and RL training; \textbf{Meow-8B-SFT-GRPO} surpassed SurveyX (35.62 vs.\ 29.60 LLM-Judge total) and beat GPT-5 Nano, DeepSeek-R1, and Gemini 2.5 Flash-Lite on the SurveyX test set.
\end{itemize}

\vspace{4pt}
\entry{Lakala Payment \,\textemdash\, Data Engineering Intern}{Beijing, China}{Jul 2024 -- Aug 2024}{}
\begin{itemize}
  \item Assisted in the development and maintenance of the company's internal data platform using Hadoop ecosystem tools.
  \item Designed and developed the internal data platform's data quality monitoring system.
\end{itemize}

\vspace{4pt}
\entry{Beijing Academy of Artificial Intelligence (BAAI) \,\textemdash\, Research Intern}{Beijing, China}{Jun 2023 -- Oct 2023}{}
\begin{itemize}
  \item Contributed to BAAI's 3D electron-microscopy (EM) processing toolchain, focusing on advanced neuron-segmentation methodologies including PyTorch Connectomics (PyTC) and Local Shape Descriptors (LSD).
  \item Built reproducible training pipelines for large-volume connectomics data, covering preprocessing, augmentation, and patch-based inference for cubic-micron EM volumes.
  \item Optimized segmentation models via systematic hyperparameter tuning combining Grid Search and Bayesian Optimization, materially improving segmentation quality on benchmark volumes.
\end{itemize}

\vspace{4pt}
\entry{Tencent \,\textemdash\, Machine Learning Engineering Intern}{Tencent Video, Shenzhen, China}{Jun 2022 -- Aug 2022}{}
\begin{itemize}
  \item Independently owned an end-to-end ML project to surface high-potential video categories on the Tencent Video platform, from data extraction and cleaning through algorithm design, evaluation, and stakeholder reporting.
  \item Built scalable data pipelines on Tencent's internal task-scheduling platform, handling dependency resolution across heterogeneous data sources.
  \item Engineered an XGBoost-based scoring model producing quantitative indicators of video-category potential; tuned the model with cross-validated hyperparameter search.
  \item Wrote production SQL and Python against large-scale internal data warehouses to extract, join, and transform features at scale.
  \item Deployed Spark for distributed feature engineering and model scoring, keeping the pipeline tractable on volumes of up to \textbf{7,500,000 records}.
  \item Synthesized findings into two project reports that informed downstream content-strategy and operational decisions on Tencent Video.
\end{itemize}

% ============== PROJECTS ==============
\section{PROJECTS}

\entry{Music Chat Recommender \,\textemdash\, LLM-mediated multi-turn recommender}{\href{https://huggingface.co/spaces/Cedric1218/music-chat-recommender}{Live Demo} \,\textbar\, \href{https://github.com/cedricshan/music-chat-recommender}{GitHub}}{Apr 2026}{}
\begin{itemize}
  \item Built a chat-first music recommender that parses free-form English requests (e.g.\ ``sad songs for a rainy evening, but no Coldplay''), runs live searches, and returns an ordered short-list with embedded YouTube playback.
  \item Designed a \textbf{two-call LLM architecture}: an intent-parsing call extracts a Pydantic-typed \texttt{SearchQuery} (mood, genres, exclusions, year range, control flags) from the latest user turn plus a serialized memory; a rerank-and-reply call selects from the candidate pool and writes the human-facing reply, with both outputs validated against Pydantic schemas to make malformed LLM outputs unrecoverable failures rather than crashes.
  \item Implemented a \textbf{provider abstraction} over \textbf{Groq Llama 3.3 70B} (primary, JSON mode) and \textbf{Gemini 2.5 Flash-Lite} (fallback) to absorb mid-project free-tier policy changes from both Spotify (API deprecation, Nov 2024) and Google.
  \item Pivoted the music backend from Spotify to the keyless \textbf{iTunes Search API} after the Spotify Web API was restricted; reconstructed similarity reasoning from search alone via a fan-out strategy that issues 1--6 facet-specific queries per intent.
  \item Built per-session \texttt{ConversationState} (likes, dislikes, must-exclude artists, history) so follow-ups like ``stop recommending Drake'' and ``more diverse next time'' work without restating context; orchestrated everything in a single Gradio app deployed publicly on Hugging Face Spaces.
\end{itemize}

\vspace{4pt}
\entry{Age-Dependent Heterogeneity in the PA -- Mental-Distress Association}{Causal ML on BRFSS 2015--2024 \,\textbar\, \href{https://github.com/cedricshan/pa-fmd-hte}{GitHub}}{Apr 2026}{}
\begin{itemize}
  \item Pooled \textbf{ten consecutive annual waves} of the U.S.\ Behavioral Risk Factor Surveillance System (BRFSS, 2015--2024; \textbf{n $=$ 3{,}242{,}218} adults after complete-case filtering) to test whether the protective association between leisure-time physical activity (PA) and frequent mental distress (FMD) varies systematically by age.
  \item Fit \textbf{survey-weighted logistic regression} with raked sampling weights, sandwich SEs clustered on PSU, and a formal PA $\times$ Age likelihood-ratio test for effect modification; ran age-stratified models within each of six age groups and a three-way PA $\times$ Age $\times$ Year interaction for temporal change.
  \item Independently estimated heterogeneous treatment effects via \textbf{Causal Forest under Double Machine Learning} (\texttt{CausalForestDML} in EconML), with HistGradientBoosting nuisance models and 2-fold cross-fitting, recovering the conditional ATE as a function of covariates without pre-specifying subgroups.
  \item \textbf{Found a striking, monotonic age gradient}: PA odds ratio for FMD ranges from \textbf{0.89} (ages 18--24) to \textbf{0.50} (ages 55--64); the Causal Forest independently identifies \textbf{age as the dominant heterogeneity driver} (feature importance $=$ 0.39, $2.5\times$ the next predictor).
  \item \textbf{Documented a novel temporal finding}: the already-weak protective effect among 18--24-year-olds has been eroding over the decade, reaching the null in both \textbf{2018 and 2024} and paralleling the deepening youth mental-health crisis.
  \item Validated robustness with \textbf{E-values} for unmeasured confounding, propensity-score overlap diagnostics, a placebo test on a non-causal outcome, and a conditional-imputation sensitivity analysis on missing income.
\end{itemize}

\vspace{4pt}
\entry{Optimizing Turbine Blade Design under Operational Uncertainty}{Robust DOE + Surrogate Modeling \,\textbar\, \href{https://github.com/cedricshan/Optimizing-Turbine-Blade-Design}{GitHub}}{Apr 2026}{}
\begin{itemize}
  \item Tackled a \textbf{constrained robust optimization} problem on a finite-element gas-turbine-blade simulator: minimize expected maximum von Mises stress subject to a strict displacement feasibility constraint ($d < 1.3\times10^{-3}$\,m), under uncontrollable perturbations of cooling temperature ($\pm 2^{\circ}\text{C}$) and pressure load ($\pm 10^4$\,Pa), all within a hard \textbf{300-evaluation simulation budget}.
  \item Designed a \textbf{four-phase pipeline}: (i) 100-point maximin Latin Hypercube Design over the 6-D unit hypercube; (ii) Gaussian Process surrogate with \textbf{Mat\'ern-5/2 kernel and ARD length-scales}, achieving \textbf{10-fold CV $R^{2}>0.994$} on both stress and displacement; (iii) 150 sequential runs driven by an \textbf{Expected Improvement with Constraints} acquisition, augmented by a Gaussian proximity penalty for batch diversification; (iv) 27-run robust grid validation ($3\times3$ perturbation grid on 3 candidates) plus 23 random validation runs.
  \item Achieved a \textbf{41\% reduction} in maximum stress relative to the LHD best, with the recommended design satisfying displacement feasibility on \textbf{100\%} of all tested perturbations and a \textbf{45\% safety margin} below the failure threshold; ARD length-scale analysis isolated \textbf{CTE} (Coefficient of Thermal Expansion) as the dominant design factor.
  \item Built a three-stage \textbf{SLURM pipeline} on the Duke Computing Cluster (input generation $\rightarrow$ array-job parallel simulation with \texttt{--array=1-N\%40} $\rightarrow$ chained result merging via \texttt{--dependency=afterok}); 40-way parallelism delivered a \textbf{$\sim$33$\times$ wall-clock speedup} (4 min vs.\ 2.2 h for a 100-run batch), enabling rapid sequential iteration.
\end{itemize}

\vspace{4pt}
\entry{Paper Helicopter --- Sequential DOE}{STA 643 \,\textbar\, \href{https://github.com/cedricshan/Paper-Helicopter-DOE}{GitHub}}{Apr 2026}{}
\begin{itemize}
  \item End-to-end design optimization via fractional-factorial screening, confirmation runs, response-surface (RSM) optimization, and validation experiments.
\end{itemize}

\vspace{4pt}
\entry{Bradley--Terry Analysis of the English Premier League}{\href{https://docs.google.com/presentation/d/1mncW87F79ezDnqah3qGSjqWAFXMQzGMNqfB2MTYl6jM/edit}{Slides} \,\textbar\, \href{https://github.com/cedricshan/Bradley-Terry-Model-Analysis-of-the-English-Premier-League}{GitHub}}{Mar 2026}{}
\begin{itemize}
  \item Applied the \textbf{Bradley--Terry} paired-comparison framework to \textbf{7{,}860} EPL match results across 21 seasons (2005/06--2025/26, 44 clubs) to estimate relative team strengths and quantify home advantage; reformulated the base BT model as logistic regression to enable standard MLE inference and asymptotic Wald / likelihood-ratio tests.
  \item Extended the analysis with the \textbf{Davidson} formulation to absorb the 24\% of matches ending in draws, plus \textbf{season-specific} and \textbf{team-specific} home-advantage intercepts; validated each extension via nested LRT and AIC comparison.
  \item Estimated the home-team odds boost at $\hat{\theta}\!\approx\!1.64\times$ ($p\!<\!10^{-15}$ under all model variants); team-strength estimates from BT and Davidson agreed at $r\!=\!0.990$, confirming robustness.
  \item Detected a \textbf{significant secular decline} in home advantage over the study window and a \textbf{near-complete collapse} during the 2020/21 spectator-less COVID season ($\hat{\alpha}\!\approx\!-0.10$) --- direct empirical support for the causal role of crowds.
\end{itemize}

\vspace{4pt}
\entry{HIV Self-Testing Study --- Reproduction}{Reproducibility in Public Health \,\textbar\, \href{https://github.com/cedricshan/HIV-Self-Testing-Study-Reproduce}{GitHub}}{Jan 2026}{}
\begin{itemize}
  \item Careful reproduction of a published HIV self-testing study, validating statistical methodology, effect estimates, and robustness checks.
\end{itemize}

\vspace{4pt}
\entry{Survey Outline Evaluation Benchmark}{Companion code to ICASSP 2026 \,\textbar\, \href{https://github.com/cedricshan/Survey-Outline-Evaluation-Benckmark}{GitHub}}{Sep 2025}{}
\begin{itemize}
  \item End-to-end pipeline for generating and evaluating academic survey outlines with LLMs --- multi-dimensional metrics, statistical analysis, and a public benchmark.
\end{itemize}

\vspace{4pt}
\entry{Football Transfer Market Visualization}{Team Leader (3-person team) \,\textbar\, \href{https://transfer-market-vis.netlify.app/}{Live Demo} \,\textbar\, \href{https://github.com/cedricshan/Football-Transfer-Market-Visualization}{GitHub}}{Sep 2023 -- Oct 2023}{}
\begin{itemize}
  \item Led a 3-person STATS 401 team end-to-end: scoped the research questions, defined the data model, and split engineering and design responsibilities.
  \item Wrote the full Python data-cleaning pipeline; designed the interactive UI and visual encoding from scratch in D3.js, letting users drill down by club, season, and league.
  \item Shipped a publicly hosted visualization at \href{https://transfer-market-vis.netlify.app/}{transfer-market-vis.netlify.app}.
\end{itemize}

\vspace{4pt}
\entry{Internal Data Quality Monitoring System}{Independent project \,\textbar\, \href{https://github.com/cedricshan/Data-Quality-Mnitoring-System}{GitHub}}{Jul 2024}{}
\begin{itemize}
  \item Python-based data-quality monitoring system designed for large-scale data environments; uses statistical methods to evaluate data quality and triggers alerts when anomalies are detected.
\end{itemize}

% ============== HONORS ==============
\section{HONORS \& AWARDS}
\begin{itemize}
  \item Dean's List with Distinction, Duke Kunshan University.
  \item Finalist Prize, Interdisciplinary Contest in Modeling (MCM/ICM).
  \item First Prize, National Olympiad in Informatics in Provinces (NOIP).
  \item Outstanding Peer Mentor and Outstanding Peer Tutor, Duke Kunshan University (2022--2024).
  \item Best Volunteer, 7th China Buyout Fund Annual Conference, Chinese Museum of Funds.
\end{itemize}

% ============== LEADERSHIP ==============
\section{LEADERSHIP \& SERVICE}
\begin{itemize}
  \item \textbf{Technical Intern}, Beijing 2022 Olympic \& Paralympic Winter Games --- Organising Committee. \hfill {\small\color{soft} Dec 2021 -- Jan 2022}\\
  Conducted statistical analysis of the IOC global technical partners' transportation demands during pre-Games operations; compiled briefing materials informing vehicle allocation and route planning.
  \item \textbf{Volunteer}, Duke China-U.S.\ Summit 2023 Committee. \hfill {\small\color{soft} Jun 2023 -- Jul 2023}
  \item \textbf{Student Leader}, Kunshan Student Orientation Peers (KSOP) at Duke. \hfill {\small\color{soft} Nov 2022 -- May 2023}
\end{itemize}

% ============== SKILLS ==============
\section{TECHNICAL SKILLS}

\noindent
\textbf{\color{ink}Programming Languages:}\, Python, R, SQL, JavaScript (D3.js), Bash.\\[3pt]
\textbf{\color{ink}Machine Learning \& LLM:}\, PyTorch, HuggingFace Transformers, vLLM, TRL, LoRA / PEFT, DeepSpeed, XGBoost, scikit-learn.\\[3pt]
\textbf{\color{ink}Data \& Infrastructure:}\, Hadoop, Spark, Causal Forests, Bayesian Optimization, Design of Experiments, Bradley--Terry models.\\[3pt]
\textbf{\color{ink}Tools:}\, Git, LaTeX, Gradio, Linux, Jupyter.\\[3pt]
\textbf{\color{ink}Languages:}\, English (professional working proficiency), Mandarin Chinese (native).

\end{document}
