% ============================================================
%  Yuan Shan — Resume (1 page)
%  Compile with: tectonic resume.tex
% ============================================================
\documentclass[10.5pt,letterpaper]{article}

\usepackage[margin=0.5in,top=0.4in,bottom=0.4in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}

\renewcommand{\familydefault}{\sfdefault}

% ---------- palette ----------
\definecolor{accent}{HTML}{8A3324}
\definecolor{ink}{HTML}{1C1C21}
\definecolor{muted}{HTML}{555560}
\definecolor{soft}{HTML}{8A8A95}

\hypersetup{colorlinks=true, urlcolor=accent, linkcolor=accent}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ---------- section style ----------
\titleformat{\section}
  {\normalsize\bfseries\color{accent}}
  {}{0pt}{}
  [\vspace{-5pt}{\color{accent}\rule{\textwidth}{0.6pt}}]
\titlespacing*{\section}{0pt}{6pt}{2pt}

% ---------- list defaults ----------
\setlist[itemize]{
  leftmargin=1em,
  topsep=0pt,
  parsep=0pt,
  itemsep=1pt,
  label=\textcolor{accent}{\textbullet}
}

% ---------- entry helper ----------
% \entry{Title}{Subtitle}{Right top}{Right bottom}
\newcommand{\entry}[4]{%
  \noindent\textbf{\color{ink}#1}\hfill{\color{soft}\small #3}\\[0pt]%
  \textit{\color{muted}#2}\hfill\textit{\color{soft}\small #4}%
  \vspace{1pt}%
}

% ---------- compact entry: just title with right-aligned date ----------
\newcommand{\eduentry}[4]{%
  \noindent\textbf{\color{ink}#1}, {\color{muted}#2}\hfill{\color{soft}\small #3}\\[1pt]%
  \textit{\color{muted}\small #4}%
  \vspace{2pt}%
}

\begin{document}

% ============== HEADER ==============
\begin{center}
  {\fontsize{22}{26}\selectfont\bfseries\color{ink} Yuan Shan}\\[2pt]
  {\small\color{muted} M.S.\ in Statistical Science\, $\cdot$\, Duke University}\\[4pt]
  {\footnotesize\color{muted}
    \href{mailto:ys328@duke.edu}{ys328@duke.edu}
    \;$\cdot$\; (919) 697-2488
    \;$\cdot$\; \href{https://github.com/cedricshan}{github.com/cedricshan}
    \;$\cdot$\; \href{https://www.linkedin.com/in/yuanshan20011218/}{linkedin.com/in/yuanshan20011218}
    \;$\cdot$\; \href{https://cedricshan.github.io}{cedricshan.github.io}
  }
\end{center}

% ============== EDUCATION ==============
\section{EDUCATION}

\entry{Duke University}{M.S.\ in Statistical Science}{Aug 2024 -- May 2026}{Durham, NC, USA}\\
\entry{Duke Kunshan University}{B.S.\ in Data Science (Interdisciplinary Studies)}{Jul 2020 -- Aug 2024}{Kunshan, China}

% ============== EXPERIENCE ==============
\section{EXPERIENCE}

\entry{Wenge Tech \,\textemdash\, LLM Algorithm Engineer Intern}{Beijing \,$\cdot$\, {\small\color{accent}\itshape Work accepted at IEEE ICASSP 2026}}{May 2025 -- Oct 2025}{}
\begin{itemize}
  \item Designed and built \textbf{MEOW}, the first metadata-driven, end-to-end LLM framework for academic survey outline generation, combining SFT with reinforcement learning (\textbf{GRPO}) under RLHF.
  \item Constructed a public benchmark and multi-dimensional metrics (structure, content, pragmatics); curated $\sim$20k+ surveys from arXiv, bioRxiv, medRxiv with Chain-of-Thought annotations.
  \item Optimized \textbf{Qwen3-8B} (full and LoRA); designed reward functions on structural distance and format compliance to align with human writing preferences.
  \item Leveraged \textbf{vLLM} for inference and RL training acceleration, achieving \textbf{state-of-the-art} results over SurveyX, GPT-5 Nano, and DeepSeek-R1 on the benchmark.
\end{itemize}

\vspace{2pt}
\entry{Tencent \,\textemdash\, Machine Learning Engineering Intern}{Tencent Video}{Jun 2022 -- Aug 2022}{}
\begin{itemize}
  \item Independently owned an end-to-end ML project to surface high-potential video categories on Tencent Video, from data extraction and cleaning through model design and stakeholder reporting.
  \item Engineered an \textbf{XGBoost}-based scoring model producing quantitative indicators of video-category potential; tuned via cross-validated hyperparameter search.
  \item Built scalable pipelines on Tencent's internal task-scheduling platform; used \textbf{Spark} for distributed feature engineering on volumes up to \textbf{7.5M records}.
  \item Wrote production SQL/Python; authored two reports informing Tencent Video's content-strategy decisions.
\end{itemize}

% ============== PROJECTS ==============
\section{SELECTED PROJECTS}

\entry{Music Chat Recommender}{Multi-turn LLM chatbot \,\textbar\, \href{https://huggingface.co/spaces/Cedric1218/music-chat-recommender}{HuggingFace Space}}{Apr 2026}{}
\begin{itemize}
  \item Built a multi-turn LLM chatbot for personalized music recommendations with \textbf{Gradio} + \textbf{Groq Llama 3.3 70B}, integrating iTunes Search and YouTube Data APIs.
  \item Deployed a public live demo on Hugging Face Spaces; designed conversation state, retrieval, and ranking logic end-to-end.
\end{itemize}

\vspace{2pt}
\entry{Bradley--Terry Analysis of the English Premier League}{Sports Analytics \,\textbar\, \href{https://docs.google.com/presentation/d/1mncW87F79ezDnqah3qGSjqWAFXMQzGMNqfB2MTYl6jM/edit}{Slides}}{Mar 2026}{}
\begin{itemize}
  \item Estimated latent team strengths across multiple Premier League seasons via the \textbf{Bradley--Terry} model and quantified home-field advantage over time.
  \item Implemented model fitting, diagnostics, and visualization in Python/Jupyter; presented findings in a deck for an applied-statistics seminar.
\end{itemize}

% ============== SKILLS ==============
\section{SKILLS}
\noindent
\textbf{\color{ink}Programming:}\, Python, R, SQL, JavaScript (D3.js), Bash. \quad
\textbf{\color{ink}ML / LLM:}\, PyTorch, Transformers, vLLM, TRL, LoRA / PEFT, DeepSpeed, XGBoost.\\[1pt]
\textbf{\color{ink}Data \& Infra:}\, Hadoop, Spark, Bayesian Opt., Causal Forests, DOE. \quad
\textbf{\color{ink}Languages:}\, English (professional), Mandarin (native).

% ============== HONORS ==============
\section{HONORS}
\noindent
Dean's List with Distinction, Duke Kunshan University \,$\cdot$\, Finalist Prize, Mathematical Contest in Modeling (MCM) \,$\cdot$\, First Prize, National Olympiad in Informatics in Provinces (NOIP)

\end{document}
